\href{http://www.sigcomm.org/content/ebook}{Recent Advances in Networking}

### 2013-08-06 Compiled/chapter7/router.tex
Full compiled
links for chapter 7

\clearpage
\section{Router-level topology}
\label{sec:router}

@@

\clearpage
{\bf Lesson 1:} {\em Due to the absence of accurate and rigorous methods for solving the IP alias
resolution problem, the actual values of the connectivity of each router (\ie node degrees)
inferred from traceroute measurements cannot be taken at face
value.}

>>>>

%\clearpage
\section{Router-level topology}
\label{sec:router}

@@

%\clearpage
{\bf Lesson 1:} {\em Due to the absence of accurate and rigorous methods for solving the IP alias
resolution problem, the actual values of the connectivity of each router (\ie node degrees)
inferred from traceroute measurements cannot be taken at face
value.}
